### 2010-03-17 papers/icfp-2010-desc/paper_idesc.tex
IDesc@ICFP: better intro to Fin's constrained presentation
IDesc@ICFP: move Desc factorization to IDesc. Give a new reason for doing so.

@@

In order to code this data-type, we have to appeal to equality:

>>>>

\subsection{Desc, atomically}

\begin{wstructure}
<- Adding hindx have introduced some duplication
    <- indx == hindx 1
    -> We can factor out commonalities 
        /> Obtain an equivalent presentation
        /> Still embeddable (refer to the Agda model)
\end{wstructure}

Before moving on indexed descriptions, we have to carry out some
maintenance work on descriptions. We presented $\Desc$ as the grammar
of inductive types. Hence, the codes closely follow this grammar. In
the following, we adopt an alternative presentation. With $\DSigma$,
we are already quoting a standard type-former. In the alternative
presentation, we go further and entirely present our codes as
quotation of standard type-formers. This presentation is shown in
Figure~\ref{fig:type-former-desc}.

This reorganisation is strictly equivalent to the previous one
(Fig.~\ref{fig:hindx_desc}). Just as the previous version, it is also
self-descriptive. We refer the reader to the companion technical
report for details. In this finer-grained presentation, we can define
$\DIndx$ and $\DHindx$ as follow:

\[\begin{array}{l@{\:\mapsto\:\:}l}
\DIndx{D}         & \DProd{\DId}{D}                      \\
\DHindx{H}{D}     & \DProd{(\DPi{H}{(\LAM{\_} \DId)})}{D}
\end{array}
\]

Consequently, the examples previously developed can be
straightforwardly translated into this new presentation. \note{We
  might want to re-do the Nat example here, as we encode once again in
  $\IDesc$} In the following, we adopt this last version as our de
facto universe of inductive types. In particular, we are going to
evolve this presentation into an indexed one.

\note{Shall we talk about the Type Theory being Desc Zero? or such story?}

\[
\begin{array}{ll}
\stk{
\data \Desc : \Set \where \\
\;\;\begin{array}{@{}l@{\::\:}l@{\quad}l}
    \DId            & \Desc                                   \\
    \DUnit          & \Desc                                   \\
    \DProd{}{}      & \PI{\V{D}, \V{D'}}{\Desc} \Desc         \\
    \DSigma         & \PI{\V{S}}{\Set} \PIS{S \To \Desc} \Desc \\
    \DPi            & \PI{\V{S}}{\Set} \PIS{S \To \Desc} \Desc 
\end{array}
}
&
\stk{
\descop{\_\:}{} : \Desc \To \Set \To \Set \\
\begin{array}{@{}l@{\:=\:\:}ll}
\descop{\DId}{X}          &  X                                           \\
\descop{\DUnit}{X}        &  \Unit                                       \\
\descop{\DProd{D}{D'}}{X} &  \TIMES{\descop{D}{X}}{\descop{D'}{X}}       \\
\descop{\DSigma{S}{D}}{X} &  \SIGMA{\V{s}}{S} \descop{D\: s}{X}                \\
\descop{\DPi{S}{D}}{X}    &  \PI{\V{s}}{S} \descop{D\: s}{X}            
\end{array}
}
\end{array}
\]

\caption{Universe of descriptions based on Type-formers}
\label{fig:type-former-desc}

@@

One way to code constrained data-type is to appeal to equality. The
constraints are therefore captured by equations in the data-type. In
this case, we obtain the following definition:
